Enforced Invariant Confluence

### 2018-02-26 doc/paper_redux/sufficient_conditions.tex
Added monotonicity proof.

>>>>

As a special case, \clmref{statebasedsufficient} tells us that a set $T$ of
transactions is \Iconfluent{} if $I$ is monotonic and $O$ is a semilattice.

\begin{claim}\clmlabel{monotonicity}
  Let $O = (S, s_0, \join)$ be a state-based object where $(S, \join)$ is a
  semilattice. Let $s \leq s' \defeq s \join s' = s'$. Let $T$ be an arbitrary
  set of transactions. Let $I$ be a \defword{monotonic}: for all $s, s'\in S$,
  if $s \leq s'$ and $I(s)$, then $I(s')$. Also assume $I(s_0)$. $T$ is
  \Iconfluent{}.
\end{claim}
\begin{elidableproof}
  Let $s_1$ and $s_2$ be arbitrary states such that $I(s_1)$ and $I(s_2)$. $s_1
  \leq s_1 \join s_2$, so by monotonicity, $I(s_1 \join s_2)$. Thus, by
  \clmref{statebasedsufficient}, $T$ is \Iconfluent{}.
\end{elidableproof}
